A scalar Poincaré map for anti-phase bursting in coupled inhibitory neurons with synaptic depression.

### 2022-05-03 tex/manuscript.tex
Add vertical stripes in bif diagram to show bistability

% Define some convenience commands
\renewcommand{\d}{\mathrm{d}}
\renewcommand{\k}{\mathrm{K}}
\newcommand{\ca}{\mathrm{Ca}}
\newcommand{\na}{\mathrm{Na}}
\newcommand{\leak}{\mathrm{L}}
\newcommand{\dstar}{d^\star}
\newcommand{\gstar}{g^\star}
\newcommand{\gbar}{\bar g}
\newcommand{\delt}{\Delta t}
\newcommand{\taus}{\tau_s}
\newcommand{\dn}{\delta_n}
\newcommand{\taud}{\tau_d}

@@

\begin{figure}[h!]
  \centering
  \includegraphics{burst-sols}
  \caption{Voltage traces of both cells of numerically stable solutions for increasing
    values of the coupling strength $\gbar$ (increasing top to
    bottom).~\label{fig:burst-sols}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{bif-diagram}
  \caption{Numerically computed bifurcation diagram of the cycle period of stable $n:n$ solutions for increasing coupling strength $\gbar$. Dashed lines show the interval between the $5-5$ and the suppressed solution, where higher period $n:n$ solutions occur on increasingly smaller intervals of $\gbar$.\label{fig:bif-diagram}}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics{free-quiet}
  \caption{Schematic diagram of the active and silent phases for a $3:3$ solution.
    $\bm{\mathrm{(A)}}$ Membrane potentials of cell 1 ($v_{1}$) and cell 2 ($v_{2}$).
    Grey patches depict $\delt$ intervals.
    $\bm{\mathrm{(B)}}$ Total synaptic conductance of cell 1 ($\gbar s_1$) as it crosses the release conductance $g^{\star}$.
    $\bm{\mathrm{(C)}}$ Solution $d_1(t)$ of depression variable of cell 1, during active (blue) and silent phases (orange).~\label{fig:free-quiet}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{delta-t}
  \caption{Numerically computed bifurcation diagram of $\delt$ for varying $\gbar$.
    Each continuous branch is associated with a stable $n:n$ burst solution. Increasing
    $\gbar$ increases $\Delta t$ until the solutions bifurcate at $\Delta t\approx
    T_{s}$.~\label{fig:delta-t}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{FQ-maps}
  \caption{Maps $F_n$ $\bm{\mathrm{(A)}}$ and $Q_n$ $\bm{\mathrm{(B)}}$ for
  $\gbar=0.5$ $\si{mS/cm^{2}}$ and $n=1,2,3,4$. Curves $F_n$ intersect at
  $d^{\star}=d_{s}$ which is indicated by a dashed vertical line. Curves $Q_n$ intersect at $\Delta t = \tau_{\kappa}\ln\Big(\bar g / g^{\star}\Big)$. \label{fig:FQ-maps}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{Pn-map}
  \caption{Map $\Pi_{n}:d^{\star}\mapsto d^{\star}$. $\bm{\mathrm{(A)}}$ $\Pi_{n}$ for $n=1,2,3,4$
  at $\gbar=0.5$ $\si{mS/cm^{2}}$. $\bm{\mathrm{(B)}}$ $\Pi_{2}$ with $n=2$ for
  various $\gbar$. The identity function is illustrated by a diagonal line.~\label{fig:Pn-map}}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.8\textwidth]{final-bif}
  \caption{Bifurcation diagram of the period of stable $n:n$ solutions computed analytically from fixed points of $\Pi_n$, plotted on the respective intervals of $\gbar\in \big[\gbar_{\mathcal{L}}(n),\gbar_{\mathcal{R}}(n)\big]$ (blue), and computed from numerical integrations of the ODEs (orange).~\label{fig:final-bif}}
\end{figure}

>>>>

% Define some convenience commands
\renewcommand{\d}{\mathrm{d}}
\renewcommand{\k}{\mathrm{K}}
\newcommand{\ca}{\mathrm{Ca}}
\newcommand{\na}{\mathrm{Na}}
\newcommand{\leak}{\mathrm{L}}
\newcommand{\dstar}{d^\star}
\newcommand{\gstar}{g^\star}
\newcommand{\bar g}{\bar g}
\newcommand{\delt}{\Delta t}
\newcommand{\taus}{\tau_s}
\newcommand{\dn}{\delta_n}
\newcommand{\taud}{\tau_d}

@@

\begin{figure}[h!]
  \centering
  \includegraphics{burst-sols}
  \caption{Voltage traces of both cells of numerically stable solutions for increasing
    values of the coupling strength $\bar g$ (increasing top to
    bottom).~\label{fig:burst-sols}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{bif-diagram}
  \caption{Numerically computed bifurcation diagram of the cycle period of stable $n:n$ solutions for increasing coupling strength $\bar g$. Regions of bistability are indicated by light blue vertical stripes. Dashed lines show the interval between the $5:5$ and the suppressed solution, where higher period $n:n$ solutions occur on increasingly smaller intervals of $\bar g$.\label{fig:bif-diagram}}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics{free-quiet}
  \caption{Schematic diagram of the active and silent phases for a $3:3$ solution.
    $\bm{\mathrm{(A)}}$ Membrane potentials of cell 1 ($v_{1}$) and cell 2 ($v_{2}$).
    Grey patches depict $\delt$ intervals.
    $\bm{\mathrm{(B)}}$ Total synaptic conductance of cell 1 ($\bar g s_1$) as it crosses the release conductance $g^{\star}$.
    $\bm{\mathrm{(C)}}$ Solution $d_1(t)$ of depression variable of cell 1, during active (blue) and silent phases (orange).~\label{fig:free-quiet}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{delta-t}
  \caption{Numerically computed bifurcation diagram of $\delt$ for varying $\bar g$.
    Each continuous branch is associated with a stable $n:n$ burst solution. Increasing
    $\bar g$ increases $\Delta t$ until the solutions bifurcate at $\Delta t\approx
    T_{s}$.~\label{fig:delta-t}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{FQ-maps}
  \caption{Maps $F_n$ $\bm{\mathrm{(A)}}$ and $Q_n$ $\bm{\mathrm{(B)}}$ for
  $\bar g=0.5$ $\si{mS/cm^{2}}$ and $n=1,2,3,4$. Curves $F_n$ intersect at
  $d^{\star}=d_{s}$ which is indicated by a dashed vertical line. Curves $Q_n$ intersect at $\Delta t = \tau_{\kappa}\ln\Big(\bar g / g^{\star}\Big)$. \label{fig:FQ-maps}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{Pn-map}
  \caption{Map $\Pi_{n}:d^{\star}\mapsto d^{\star}$. $\bm{\mathrm{(A)}}$ $\Pi_{n}$ for $n=1,2,3,4$
  at $\bar g=0.5$ $\si{mS/cm^{2}}$. $\bm{\mathrm{(B)}}$ $\Pi_{2}$ with $n=2$ for
  various $\bar g$. The identity function is illustrated by a diagonal line.~\label{fig:Pn-map}}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.8\textwidth]{final-bif}
  \caption{Bifurcation diagram of the period of stable $n:n$ solutions computed analytically from fixed points of $\Pi_n$, plotted on the respective intervals of $\bar g\in \big[\bar g_{\mathcal{L}}(n),\bar g_{\mathcal{R}}(n)\big]$ (blue), and computed from numerical integrations of the ODEs (orange).~\label{fig:final-bif}}
\end{figure}
